---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r}
library(tidyverse)
library(haven)
library(mirt)
library(lavaan)
set.seed(0728)
polity <- read_sav("../data/polity5/p5v2018.sav")

load("../data/wvs-longitudinal/WVS_TimeSeries_1981_2022_Rdata_v3_0.rdata")
dat_wvs <- WVS_TimeSeries_1981_2022_spss_v3_0
```


# Prepare Data
```{r}
wvs <- dat_wvs %>% dplyr::select(
  E001,
  E003,
  E005,
  E226,
  E229,
  E233,
  E224,
  E227,
  E230,
  E231,
  E233A,
  COUNTRY_ALPHA,
  COW_ALPHA,
  COW_NUM,
  S002VS,
  S020
)
wvs$proj <- "wvs"

var_clean <- function(x) {
  ifelse(x %in% c(-5, -4, -3, -2, -1), NA_real_, x) #NA_real_是double缺失值，NA是逻辑缺失值
}

var_binary <- function(x) {
  case_when(
    x %in% c(0, 1, 2, 3, 4, 5) ~ 0,
    x %in% c(6, 7, 8, 9, 10) ~ 1,
  )
}


wvs <- wvs %>%
  mutate(across(c(
    E226,
    E229,
    E233,
    E224,
    E231,
    E227,
    E230,
    E233A,
    E001,
    E003,
    E005
  ), var_clean)) %>%
  mutate(across(c(
    E226,
    E229,
    E233,
    E231,
    E224,
    E227,
    E230,
    E233A
  ), var_binary))
# performance
wvs$E001R <- wvs$E001
wvs$E003R <- wvs$E003
wvs$E005R <- wvs$E005

wvs$E001R <- ifelse(wvs$E001R == 1, 1, 0)
wvs$E003R <- ifelse(wvs$E003R == 3, 1, 0)
wvs$E005R <- ifelse(wvs$E005R == 1, 1, 0)

# procedual
wvs$E001 <- ifelse(wvs$E001 == 3, 1, 0)
wvs$E003 <- ifelse(wvs$E003 == 2 | wvs$E003 == 4, 1, 0)
wvs$E005 <- ifelse(wvs$E005 == 2 | wvs$E005 == 3, 1, 0)

# temp <- wvs
# table(temp$E226)
# table(temp$E226)
wvs_normal <- wvs

```

```{r}
procedural_democracy <- wvs_normal %>%
  dplyr::select(E226, E229, E233) %>%
  rename(
    election = E226,
    protection = E229,
    women_right = E233
  )
performance_democracy <- wvs_normal %>%
  dplyr::select(E224, E227, E230, E233A) %>%
  rename(
    rich_tax = E224,
    unempolyment_aid = E227,
    eco = E230,
    inc_euqal = E233A
  )


procedural_democracy$election <- var_clean(procedural_democracy$election)
procedural_democracy$protection <- var_clean(procedural_democracy$protection)
procedural_democracy$women_right <- var_clean(procedural_democracy$women_right)
performance_democracy$rich_tax <- var_clean(performance_democracy$rich_tax)
performance_democracy$unempolyment_aid <- var_clean(performance_democracy$unempolyment_aid)
performance_democracy$eco <- var_clean(performance_democracy$eco)
performance_democracy$inc_euqal <- var_clean(performance_democracy$inc_euqal)
```


# CFA
deprecated
```{r efa, eval= FALSE}
data_cfa <- cbind(procedural_democracy, performance_democracy)
m_cfa <- " procedural  =~ election +protection + women_right
              performance =~ rich_tax + unempolyment_aid
              "

cfa_fit <- cfa(m_cfa, data = data_cfa)
fitMeasures(cfa_fit)
summary(cfa_fit, fit.measures = TRUE, standardized = TRUE)
# RMSEA < 0.8
# SRMR <0.05

efa_fit <- cfa(m_cfa, data = data_cfa)
summary(efa_fit)


anova()
```

# IRT
```{r irt}
library(mirt)

getIrtScore <- function(data) {
  irtPref <- mirt(data, 1, itemtype = "graded", SE = FALSE) # , control=list(method="CG", maxit=5000))
  # print(summary(irtPref)$conv)
  scores <- fscores(irtPref, method = "MAP", na.rm = FALSE)
  return(scores)
}

procedural_score <- getIrtScore(procedural_democracy) %>%
  as.tibble() %>%
  rename(procedural_score = F1)
performance_score <- getIrtScore(performance_democracy) %>%
  as.tibble() %>%
  rename(performance_score = F1)



wvs_score <- bind_cols(wvs_normal, procedural_score, performance_score) %>% dplyr::select(COW_NUM, S020, procedural_score, performance_score)

wvs_score <- wvs_score %>%
  group_by(S020, COW_NUM) %>%
  summarise(
    performance = mean(performance_score, na.rm = TRUE),
    procedural = mean(procedural_score, na.rm = TRUE)
  )
# wvs_score <- wvs_score %>%
#   aggregate(.,FUN=mean,by=list(wvs_score$COW_NUM,wvs_score$S002VS)) %>%
#   select(COW_NUM,S002VS,procedural_score,performance_score) %>%
#   rename(COWcode = COW_NUM,
#          wave = S002VS) %>%
#   na.omit()
```

```{r country-year}
wvs_plot1 <- wvs_score %>%
  filter(!is.na(procedural) | !is.na(performance)) %>%
  left_join(., Vdem[, c("COWcode", "country_name")], by = c("COW_NUM" = "COWcode"))


plot1 <- ggplot(data = wvs_plot1) +
  geom_point(aes(x = country_name, y = S002VS), shape = 15, size = 2.5) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.35, vjust = 0.5)) +
  xlab("Country name") +
  ylab("Wave")
# plot1
ggsave(plot1, file = "./fig/country_year_withcensor.pdf", width = 20, height = 2.5)

# temp <-  wvs_score %>% filter(!is.na(performance_score) & !is.na(procedural_score))
# length(unique(temp$COW_NUM))

# unique(wvs_plot1$COW_NUM)

length(unique(wvs_plot1$COW_NUM))
wvs_plot2 <- wvs_score %>% filter(COW_NUM %in% unique(wvs_plot1$COW_NUM))

length(unique(wvs_plot1$S002VS))
wvs_plot2 <- wvs_score %>% filter(S002VS %in% unique(wvs_plot1$S002VS))
```

# DV
Question: To what extent is the ideal of electoral democracy in its fullest sense achieved?

Clariﬁcation: The electoral principle of democracy seeks to embody the core value of making rulers responsive to citizens, achieved through electoral competition for the electorate’s approval under circumstances when suﬀrage is extensive; political and civil society organizations can operate freely; elections are clean and not marred by fraud or systematic irregularities; and elections aﬀect the composition of the chief executive of the country. In between elections, there is freedom of expression and an independent media capable of presenting alternative views on matters of political relevance. In the V-Dem conceptual scheme, electoral democracy is understood as an essential element of any other conception of representative democracy liberal, participatory, deliberative, egalitarian, or some other.
```{r vdem}
library(mirt)
Vdem <- readRDS("../data/Vdem/VDem_12.rds")
Vdem <- Vdem %>%
  dplyr::select(v2x_polyarchy, COWcode, year, country_id, country_name, country_text_id) %>%
  rename(democracy_score = v2x_polyarchy)
dem_mood_apsr <- read.csv("../replication/democratic_mood APSR_replication/dem_mood_apsr.csv")
Vdem <- Vdem %>%
  left_join(dem_mood_apsr[, c(
    "COW_code",
    "Year",
    "lnGDP_imp",
    "lnGDP_m1",
    "GDP_cp_btw",
    "GDP_cp_within",
    "Corrup_TI_z",
    "Corrup_TI_m1",
    "Corrup_within",
    "Corrup_btw", 
    "Gini_SWIID",
    "Educ_yrs_UN",
    "Educ_yrs_m1",
    "Gini_m1"
  )],
  by = c("COWcode" = "COW_code", "year" = "Year")
  )

```


```{r old}
Vdem <- Vdem %>%
  mutate(wave = case_when(
    2017 <= year & year <= 2022 ~ 7,  #<=:less than or equal to
    2010 <= year & year <= 2015 ~ 6,
    2005 <= year & year <= 2009 ~ 5,
    2000 <= year & year <= 2004 ~ 4,
    1995 <= year & year <= 1998 ~ 3,
    1989 <= year & year <= 1991 ~ 2,
    1981 <= year & year <= 1983 ~ 1,
    TRUE ~ 0
  )) %>%
  filter(wave != 0) %>%
  dplyr::select(-c(country_text_id, country_id)) %>%
  left_join(wvs_score, by = c("COWcode" = "COW_NUM", "year" = "S020"))

Vdem_thin <- Vdem %>%
  filter(!is.na(procedural) | !is.na(performance)) %>%
  group_by(country_name, wave) %>%
  summarise(across(everything(), mean)) #across选择列语法，everything表示选择所有列，mean表示对所选择的列求平均
```


# Regresion
```{r reg}
names(Vdem)
m1 <- lm(democracy_score ~ procedural + performance, data = Vdem)
msummary(m1,output="gt", stars = TRUE)
```


```{r reg}
m2 <- lm(democracy_score ~ procedural + performance + as.factor(year) + as.factor(country_name), data = Vdem)
msummary(m2,output="gt", stars = TRUE)
```


```{r reg}
# sig
m3 <- lm(democracy_score ~ procedural + performance + as.factor(year) + as.factor(country_name) +
  as.factor(year):as.factor(country_name), data = Vdem)
msummary(m3,output="gt", stars = TRUE)
# rocedural           -0.294384   0.092781  -3.173 0.001588 **
# performance         0.193222   0.087520   2.208 0.027646 *
```


```{r reg}
m3.1 <- lm(democracy_score ~ procedural + performance + as.factor(Year) + as.factor(country_name) +
  as.factor(Year):as.factor(country_name) +
  lnGDP_imp + Corrup_TI_z + Gini_SWIID + Educ_yrs_UN, data = Vdem)
temp <- broom::tidy(m3.1)
summary(m3.1)

m3.2 <- lm(democracy_score ~ procedural + performance + as.factor(Year) + as.factor(country_name) +
  as.factor(Year):as.factor(country_name) +
  lnGDP_m1 + Corrup_TI_m1 + Educ_yrs_m1 + Gini_m1, data = Vdem)
summary(m3.2)

m3.3 <- lm(democracy_score ~ procedural + performance + as.factor(Year) + as.factor(country_name) +
  as.factor(Year):as.factor(country_name) +
  lnGDP_imp + Corrup_TI_z + Gini_SWIID + Educ_yrs_UN +
  lnGDP_m1 + Corrup_TI_m1 + Educ_yrs_m1 + Gini_m1, data = Vdem)
summary(m3.3)
```


```{r reg}
# sig
m3.4 <- lm(democracy_score ~ procedural + performance + as.factor(year) + as.factor(country_name) +
  as.factor(year):as.factor(country_name) +
  lnGDP_imp + Corrup_TI_z, data = Vdem)
msummary(m3.4,output="gt", stars = TRUE)
```


```{r reg}
# sig
m3.5 <- lm(democracy_score ~ procedural + performance + as.factor(year) + as.factor(country_name) +
  as.factor(year):as.factor(country_name) +
  lnGDP_imp + Corrup_TI_z +
  lnGDP_m1 + Corrup_TI_m1, data = Vdem)
msummary(m3.5,output="gt", stars = TRUE)
```


```{r reg}
stargazer::stargazer(m1, m2, m3, type = "text")

library(plm)
datap <- pdata.frame(Vdem_thin, c("country_name", "wave"))
names(datap)
datasp <- datap[order(datap$wave), ]
m4 <- plm(democracy_score ~ procedural + performance, data = datasp, model = "within", effect = "twoways")
summary(m4)

m5 <- plm(democracy_score ~ procedural + performance + lnGDP_imp + Corrup_TI_z + Gini_SWIID + Educ_yrs_UN, data = datasp, model = "within", effect = "twoways")
summary(m5)

# signifi
m6 <- plm(democracy_score ~ procedural + performance + lnGDP_imp + Corrup_TI_z + Gini_SWIID + Educ_yrs_UN +
  lnGDP_m1 + Corrup_TI_m1 + Educ_yrs_m1 + Gini_m1, data = datasp, model = "within", effect = "twoways")
summary(m6)


m7 <- plm(democracy_score ~ procedural + performance + lnGDP_imp + Corrup_TI_z +
  lnGDP_m1 + Corrup_TI_m1, data = datasp, model = "within", effect = "twoways")
summary(m7)

# sig
m8 <- plm(democracy_score ~ procedural + performance + GDP_cp_within + procedural +
  lnGDP_m1 + Corrup_TI_m1, data = datasp, model = "within", effect = "twoways")
summary(m8)


m9 <- plm(democracy_score ~ procedural + performance + GDP_cp_within + procedural,
  data = datasp, model = "within", effect = "twoways"
)
summary(m9)
```


# TODO
1. 诊断stan结果


